\chapter{Publicaciones}
A continuación se listan todos los trabajos relacionados con la predicción de microARN en los que se participó durante el desarrollo del doctorado.

\section*{Publicaciones en revistas}
\begin{itemize}
	\item \textbf{Yones, C. A.}, Stegmayer, G., Kamenetzky, L., \& Milone, D. H. (2015). miRNAfe: a comprehensive tool for feature extraction in microRNA
		prediction. Biosystems, 138, 1-5.
	\item Kamenetzky, L., Stegmayer, G., Maldonado, L., Macchiaroli, N., \textbf{Yones, C.}, \& Milone, D. H. (2016). MicroRNA discovery in the human
		parasite Echinococcus multilocularis from genome-wide data. Genomics, 107(6), 274-280.
	\item Stegmayer, G., \textbf{Yones, C.}, Kamenetzky, L., \& Milone, D. H. (2017). High class-imbalance in pre-miRNA prediction: a novel approach based
		on deepSOM. IEEE/ACM transactions on computational biology and bioinformatics, 14(6), 1316-1326.
	\item \textbf{Yones, C.}, Stegmayer, G., \& Milone, D. H. (2017). Genome-wide pre-miRNA discovery from few labeled examples. Bioinformatics. 34(4),
		541-549.
	\item Bugnon, L., \textbf{Yones, C.}, Milone, D. H., y Stegmayer, G. (2017). Novel som architectures for large class imbalance prediction in genome-wide
		data. Trabajo enviado a IEEE/ACM Transactions on Computational Biology and Bioinformatics.
	\item Stegmayer, G., Di Persia, L., Rubiolo, M., Gerard, M., Pividori, M., \textbf{Yones, C.}, Bugnon, L., Rodriguez, T., Raad, J., y Milone, D. (2018).
		Predicting novel microrna: a comprehensive comparison of machine learning approaches. Briefings in Bioinformatics.
	\item Bugnon, L., \textbf{Yones, C.}, Milone, D. H., y Stegmayer, G. (2018). Deep neural architectures for highly imbalanced data in bioinformatics.
		Trabajo enviado a IEEE Transactions on Neural Networks and Learning Systems, Special Issue on Recent Advances in Theory, Methodology and
		Applications of Imbalanced Learning.
	\item \textbf{Yones, C.}, Macchiaroli, N. Kamenetzky, L., Stegmayer, G., y Milone, D. (2018). Hextractor: an R package for automatic extraction of
		hairpin sequences in genome-wide data. Trabajo enviado a Bioinformatics.
\end{itemize}

\section*{Capítulo de libro}
\begin{itemize}
	\item Stegmayer, G., \textbf{Yones, C.}, Kamenetzky, L., Macchiaroli, N., \& Milone, D. H. (2017). Computational Prediction of Novel miRNAs from
		Genome-Wide Data. In Functional Genomics (pp. 29-37). Humana Press, New York, NY.
\end{itemize}

\section*{Trabajos en eventos científicos}
\begin{itemize}
	\item \textbf{Yones, C.}, Stegmayer, G., Kamenetzky, L., Milone, D. (2016). Automatic extraction of hairpin sequences from genome-wide data. ISCB Latin
		America 2016
	\item \textbf{Yones, C.}, Stegmayer, G., Kamenetzky, L., Milone, D. (2015). miRNAfe a tool for feature extraction in pre-miRNA prediction. VI Congreso
		Argentino de Bioinformática y Biologia Computacional (CAB2C)
	\item \textbf{Yones, C.}, Stegmayer, G., Milone, D. (2015). miRNAss a semi-supervised approach for microRNA prediction. VI Congreso Argentino de
		Bioinformática y Biologia Computacional (CAB2C)
\end{itemize}
